Prediction Assignment Writeup
=============================

We Load the Caret Library, and set seed.  

```{r warning=FALSE}
library(caret); library(MASS)
set.seed(12345)
```

### Reading Data

Now we read input and test data:  

```{r}
setwd("C:/Misc/R_work/data")
pmlRaw <- read.csv("pml-training.csv")
Test <- read.csv("pml-testing.csv")
```

### Feature selection

A small random sample of input data set was manually examined for feature selection.
Now, picking only the features of interest, discarding the rest.  
```{r}
cols<-names(pmlRaw) %in% c("user_name","raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp","num_window", "roll_belt", "pitch_belt", "yaw_belt", "total_accel_belt", "gyrox_belt_x", "gyrox_belt_y", "gyrox_belt_z", "accel_belt_x", "accel_belt_y", "accel_belt_z", "magnet_belt_x", "magnet_belt_y", "magnet_belt_z", "roll_arm", "pitch_arm", "yaw_arm", "total_acel_arm", "gyros_arm_x", "gyros_arm_y", "gyros_arm_z", "accel_arm_x", "accel_arm_y", "accel_arm_z", "magnet_arm_x", "magnet_arm_y", "magnet_arm_z", "roll_dumbbell", "pitch_dumbbell", "yaw_dumbbell", "total_accel_dumbbell", "gyros_dumbbell_x", "gyros_dumbbell_y", "gyros_dumbbell_z", "accell_dumbbell_x", "accel_dumbbell_y", "accel_dumbbell_z", "magnet_dumbbell_x", "magnet_dumbbell_y", "magnet_dumbbell_z", "roll_forearm", "pitch_forearm", "yaw_forearm", "total_accel_forearm", "gyros_forearm_y", "gyros_forearm_z", "accel_forearm_x", "accel_forearm_y", "accel_forearm_z", "magnet_forearm_x", "magnet_forearm_y", "magnet_forearm_z")

pmlSlim <- pmlRaw[,cols]
pmlSlim$classe <- pmlRaw$classe
```

### Partitioning data into Training set and Test set

We set aside 70% of randomly sampled data for training set, and remaining 30% data for use as Test set.  

```{r}
inTrain <- createDataPartition(y=pmlSlim$classe, p=0.7, list=FALSE)
pmlTrain <- pmlSlim[inTrain,]
pmlTest <- pmlSlim[-inTrain,]
```

### Handling missing values

Here we look for NAs to see if we need to imputed dataset using k-nearest neighbors method.
```{r}
table(complete.cases(pmlSlim))
```

As we can see, our selected features have no NAs, so data imputation is not required.

### Training prediction model

We will now train prediction model using Linear Discriminant Analysis method.

```{r warning=FALSE}
modlda <- train(classe ~ ., method="lda", data=pmlSlim)
modlda
```

We now validate our model by looking at its accuracy in classifying Test Set that we set aside.
```{r}
pred <- as.vector(predict(modlda,pmlTest))
confusionMatrix(pred,pmlTest$classe)
```

Looking at the Confusion Matrix, we note that Accuracy is >85%, and both sensitifity and specificity are >90%.

We now use our model to classify Test data.

```{r}
predTest <- as.vector(predict(modlda,Test))
results <- data.frame(cbind(Test[,160],predTest))
colnames(results) <- c("problem_id","classe")
results
```

We now write our results to output files using the script provided with the assignment instructions:

```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(predTest)
```
